### 2019-04-15 paper/paper.tex
added number for out degrees
added takeaway blurb for popularity

In addition to the number of external dependencies per package, 
we investigate how packages support dependants. The original paper 
discovered that the majority of in degrees are concentrated among a core 
minority of packages, with the majority of packages having no dependants,
a discovery that has also been observed in other software ecosystems such
as Linux and MySQL \cite{Myers:2003}. In our updated data, we discover 
that not only have these aspects held true, but the concentration of 
dependencies has actually increased. As of April 1\textsuperscript{st} 2019, 79.2\% of packages
had zero dependants, up from 72.8\% in September 2015. Meanwhile, only \%[NUMBER] of packages
had 6 or more dependants, down from \%[NUMBER] in September 2015. It is again interesting to note
that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
paper.

@@

% \section{Version Numbering and Package Adoption}
% [NEEDS MORE DATA]

>>>>

In addition to the number of external dependencies per package, 
we investigate how packages support dependants. The original paper 
discovered that the majority of in degrees are concentrated among a core 
minority of packages, with the majority of packages having no dependants,
a discovery that has also been observed in other software ecosystems such
as Linux and MySQL \cite{Myers:2003}. In our updated data, we discover 
that not only have these aspects held true, but the concentration of 
dependencies has actually increased. As of April 1\textsuperscript{st} 2019, 79.2\% of packages
had zero dependants, up from 72.8\% in September 2015. Meanwhile, only 3.2\% of packages
had 6 or more dependants, down from 3.8\% in September 2015. It is again interesting to note
that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
paper.

@@

\textbf{Takeaways.} Using \code{npm} ranks, we are able to identify successful packages 
at any point in the life-cycle of the ecosystem. We can also use these
ranks to obtain a measure of package popularity stability over time. In 
the \code{npm} ecosystem, the amount of change in the highest ranked packages
has decreased significantly since the inception of the service, with many
more recent utilities falling out of favour relative to the oldest and most
historically successful equivalents. However, there are still some relatively newer 
packages such as \code{lodash} that have managed to compete with the oldest core packages
such as \code{underscore}.
% \section{Version Numbering and Package Adoption}
% [NEEDS MORE DATA]
